Cooperative Kernels: Safe Multitasking for Blocking Algorithms on GPUs

### 2016-11-14 write-ups/PLDI/paper.tex
Oops
Tweaks.

% The queue id cannot be transmitted since it corresponds to the
% workgroup id.
>>>>>>> 65caf661ed1c47ada958a674a0605c42b495e409

@@

@@

A goal of coopeative kernels is to allow traditional, non-blocking GPU
tasks, such as graphics shaders (in programming models such as OpenGL,
Vulkan and DirectX) and regular data-parallel computational kernels,
to be co-scheduled with blocking irregular algorithms.  It is
important to note that our new model has no effect on the manner in
which these traditional GPU workloads are programmed.

Furthermore, if our cooperative language extensions are
ignored---$\offerkill$ and $\offerfork$ are treated as no-ops,
$\transmit$ annotations are ignored, and $\globalbarrier$ and
$\resizingglobalbarrier$ calls are redirected to an existing global
barrier implementation (so that no resizing occurs in the latter
case)---then cooperative kernel will behave just like its
non-cooperative counterpart would behave.  As a result, a developer
for whom today's occupancy-bound execution model suffices can upgrade
their kernel to a cooperative form and retain backwards-compatibility
with today's GPU platforms by pre-processing away our language
extensions.

>>>>

% The queue id cannot be transmitted since it corresponds to the
% workgroup id.

@@

\ADComment{Move this to the appendix.}

@@

A goal of coopeative kernels is to allow traditional, non-blocking GPU
tasks (e.g.\ graphics shaders in OpenGL, Vulkan and DirectX, and regular data-parallel computational kernels)
to be co-scheduled with blocking irregular algorithms.  It is
important to note that our new model has no effect on the manner in
which these traditional GPU workloads are programmed.

Furthermore, if our cooperative language extensions are
ignored---$\offerkill$ and $\offerfork$ are treated as no-ops,
$\transmit$ annotations are ignored, and $\globalbarrier$ and
$\resizingglobalbarrier$ calls are redirected to an existing global
barrier implementation (so that no resizing occurs in the latter
case)---then a cooperative kernel will behave just like its
non-cooperative counterpart would behave.  As a result, a developer
for whom today's occupancy-bound execution model suffices can upgrade
their kernel to a cooperative form and retain backwards-compatibility
with today's GPU platforms by pre-processing away our language
extensions.
